Interoception Scale (Study 2) - Data Cleaning

### 2025-12-29 paper/manuscript.qmd
added internal consistency for MAIA subscales
added internal consistency for BPQ and IAS

The Multidimensional Assessment of Interoceptive Awareness [MAIA-2, @mehling2018multidimensional] measures 8 dimensions with 37 items presented on a 7-point Likert scale (0 = *Never*, 6 = *Always*). It includes bodily dimensions such as Body Listening, Noticing, Emotional Awareness, dimensions related to emotion regulation, such as Trust, Not-worrying, and Self-Regulation, as well as dimensions related to attention, such as Attention Regulation and Not-Distracting. The relationship of some of these dimensions to interoception remains debated, particularly Not-Distracting and Not-Worrying, which tend to show weak or non-existent correlations with the other MAIA subscales [@ferentzi2021examining].

The Body Perception Questionnaire - Very Short Form [BPQ-VSF, @cabrera2018assessing] measures a general score of bodily awareness with 12 items presented on 5-point Likert scale (0 = *Never*, 5 = *Always*).

The Interoceptive Accuracy Scale [IAS, @murphy2020testing] measures a general score of interoceptive accuracy to physical sensations with 21 items presented on a 5-point Likert scale (1 = *Disagree Strongly*, 5 = *Strongly Agree*).

>>>>

The Multidimensional Assessment of Interoceptive Awareness [MAIA-2, @mehling2018multidimensional] measures 8 dimensions with 37 items presented on a 7-point Likert scale (0 = *Never*, 6 = *Always*). It includes bodily dimensions such as Body Listening, Noticing, Emotional Awareness, dimensions related to emotion regulation, such as Trust, Not-worrying, and Self-Regulation, as well as dimensions related to attention, such as Attention Regulation and Not-distracting. The relationship of some of these dimensions to interoception remains debated, particularly Not-Distracting and Not-Worrying, which tend to show weak or non-existent correlations with the other MAIA subscales [@ferentzi2021examining]. The subscales of the MAIA-2 showed an acceptable to good internal consistency: ωAttention regulation = 0.87, ωBody listening = 0.76, ωEmotional awareness = 0.79, ωNot-distracting = 0.80, ωNoticing = 0.68,  ωNot-worrying = 0.79, ωSelf regulation =  0.84, and ωTrusting = 0.84.

The Body Perception Questionnaire - Very Short Form [BPQ-VSF, @cabrera2018assessing] measures a general score of bodily awareness with 12 items presented on 5-point Likert scale (0 = *Never*, 5 = *Always*). Internal consistency for the BPQ-Awareness was good (ω = 0.91).

The Interoceptive Accuracy Scale [IAS, @murphy2020testing] measures a general score of interoceptive accuracy to physical sensations with 21 items presented on a 5-point Likert scale (1 = *Disagree Strongly*, 5 = *Strongly Agree*). The IAS had good internal consistency (ω = 0.88).

### 2025-12-29 study2/analysis/1_cleaning.qmd
added internal consistency for BPQ and IAS

- MAIA [x]
- MINT []
- BPQ []
- IAS []
- TAS-20 []
- B-ERS []
- CERQ-Short []
- CEFSA-14 []
- PI-18 []
- SILS (only one item)
- PHQ-4 []

>>>>

- MAIA [x]
- MINT []
- BPQ [x]
- IAS [x]
- TAS-20 []
- B-ERS []
- CERQ-Short []
- CEFSA-14 []
- PI-18 []
- SILS (only one item)
- PHQ-4 []

```{r}
bpq <- df[,grepl("^BodyAwareness_", names(df))]
bpq <- bpq[,(names(bpq) != "BodyAwareness_AttentionCheck_1")]
psych::omega(bpq, nfactors = 1)

```

```{r}
ias <- df[,grepl("^IAS_", names(df))]
ias <- ias[,(names(ias) != "IAS_AttentionCheck_1")]
psych::omega(ias, nfactors = 1)

```
